MATD02 - Exploration of Finite Geometry

### 2024-11-17 paper/main.tex
Small typo fixes

    It's fairly routine work to show the set of points and lines shown do in fact satisfy our earlier axioms,
    however more interesting is that this plane has the same number of points and all lines contain three points.
    Does this generalize to all projective spaces?

@@

    \begin{theorem}
        Given a finite projective space, there exists a positive integer $q$ such that any line in $L$ contains exactly $q+1$ elements.
        We call q the order of this space.
    \end{theorem}

@@

    In fact, when looking at projective geometry through the lens of infinite fields like $\mathbb{R}$,
    we get a definition of projective spaces from one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$ \cite{weisstein_projective_nodate}.
    Here, our dimension comes from a concept of coordinates in the underlying vector space, i.e.\ its basis.
    Working purely from axioms we don't have such an obvious idea of dimension.
    We can, however, generalize concepts from vector spaces to get the following definitions.\footnote{
        The two definitions come from Wikipedia \cite{noauthor_projective_2024},
        I could not find a text referencing them exactly, my assumption is something cited nearby states them in a modified form.
        Nevertheless, I found them fascinating as a demonstration of dimension in an abstract context.
    }

@@

        Finally, the line $xy$ contains points $y,z \in X_2$, and since $X_2$ is a subspace we must have that $xy \in X_2$
        So, $X_2$ = $P$ since any two points in $P$ form a line (containing them) that is fully contained in $X_2$.
        Thus, the dimension is at most 2.
    \end{proof}

>>>>

    It's fairly routine work to show the set of points and lines shown do in fact satisfy our earlier axioms,
    however more interesting is that this plane has the same number of points and lines, and all lines contain 3 points.
    Does this generalize to all projective spaces?

@@

    \begin{theorem}
        Given a finite projective space $(P, \mathcal{L})$, there exists a positive integer $q$ such that any line in $\mathcal{L}$ contains exactly $q+1$ elements.
        We call $q$ the order of this space.
    \end{theorem}

@@

    In fact, when looking at projective geometry through the lens of infinite fields like $\mathbb{R}$,
    we get a definition of projective spaces from one-dimensional vector subspaces of a vector space like $\mathbb{R}^n$\cite{weisstein_projective_nodate}.
    Here, our dimension comes from a concept of coordinates in the underlying vector space, i.e.\ its basis.
    Working purely from axioms we don't have such an obvious idea of dimension.
    We can, however, generalize concepts from vector spaces to get the following definitions.\footnote{
        The two definitions come from Wikipedia \cite{noauthor_projective_2024},
        I could not find a text referencing them exactly, my assumption is something cited nearby states them in a modified form.
        Nevertheless, I found them fascinating as a demonstration of dimension in an abstract context.
    }

@@

        Finally, the line $xy$ contains points $y,z \in X_2$, and since $X_2$ is a subspace we must have that $xy \in X_2$
        So $X_2$ = $P$ since any two points in $P$ form a line (containing them) that is fully contained in $X_2$.
        Thus, the dimension is at most 2.
    \end{proof}
